Finally Tagless, Partially Evaluated

### 2007-07-28 tagless/tagless-final.tex
Sorry, an even more miniscule change

The state-passing interpreter extends the CBN CPS
interpreter |RCN| of~\S\ref{S:CPS}.
\begin{code}
module RCPS(ST: sig 
  type state 
  type 'c states 
  type ('c,'sv,'dv) repr = 
      {ko: 'w. ('sv -> 'c states -> 'w) -> 'c states -> 'w}
end) = struct
  include ST
  type ('c, 'sv, 'dv) result = 'c states -> 'sv
  ... 
  let lapp e2 e1 = {ko = fun k ->
      e2.ko (fun v -> (app (lam e1) {ko = fun k -> k v}).ko k)}
  let deref () = {ko = fun k s -> k s s}
  let set e = {ko = fun k -> e.ko (fun v s -> k s v)}
  let get_res x = fun s0 -> x.ko (fun v s -> v) s0
end
\end{code}
The implementations of |int|, |app|, |lam|, and so on are
\emph{identical} to those of |RCN| and elided. New are the extended type
|repr|,
which now includes the state, and the functions
|lapp|, |deref|, and |set| representing imperative features. The
interpreter is still CBN, so evaluating |app ef ea| might not
evaluate |ea|, but evaluating |lapp ea ef| always does.
For first-order state, such as of type~$\ZZ$, we 
instantiate the interpreter as
\begin{code}
module RCPSI = RCPS(struct 
  type state = int
  type 'c states = int
  type ('c,'sv,'dv) repr = 
      {ko: 'w. ('sv -> 'c states -> 'w) -> 'c states -> 'w}
end)
\end{code}
If the state is higher-order, then the types |state| and |'c states|
are no longer be the same; furthermore, |'s states| is mutually
recursive with the type |('c,'sv,'dv) repr|, as demonstrated in the
accompanying source code.

>>>>

The state-passing interpreter extends the CBN CPS
interpreter |RCN| of~\S\ref{S:CPS}.
\begin{code}
module RCPS(ST: sig 
  type state 
  type 'c states 
  type ('c,'sv,'dv) repr = 
      {ko: 'w. ('sv -> 'c states -> 'w) -> 'c states -> 'w}
end) = struct
  include ST
  type ('c, 'sv, 'dv) result = 'c states -> 'sv
  ... 
  let lapp e2 e1 = {ko = fun k ->
      e2.ko (fun v -> (app (lam e1) {ko = fun k -> k v}).ko k)}
  let deref () = {ko = fun k s -> k s s}
  let set e = {ko = fun k -> e.ko (fun v s -> k s v)}
  let get_res x = fun s0 -> x.ko (fun v s -> v) s0
end
\end{code}
The implementations of |int|, |app|, |lam|, and so on are
\emph{identical} to those of |RCN| and elided. New are the extended type
|repr|,
which now includes the state, and the functions
|lapp|, |deref|, and |set| representing imperative features. The
interpreter is still CBN, so evaluating |app ef ea| might not
evaluate |ea|, but evaluating |lapp ea ef| always does.
For first-order state, such as of type~$\ZZ$, we 
instantiate the interpreter as
\begin{code}
module RCPSI = RCPS(struct 
  type state = int
  type 'c states = int
  type ('c,'sv,'dv) repr = 
      {ko: 'w. ('sv -> 'c states -> 'w) -> 'c states -> 'w}
end)
\end{code}
If the state has a higher-order type, then the types |state| and |'c states|
are no longer the same, and |'s states| is mutually
recursive with the type |('c,'sv,'dv) repr|, as demonstrated in the
accompanying source code.
